% In Adventu.

\hora{Ad Vesperas.} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\deusInAdiutoriumS

\vfill

\pars{Psalmus 1.}

\adventAntiphonaI

\scriptura{Psalmus 109.}

\includescore{temporalia/advent-vespers/ps109-initium-viii-G-auto.tex}

\psalmusEtTranslatio{temporalia/advent-vespers/ps109-viii-g.tex}{temporalia/advent-vespers/ps109-boh.tex}

\vfill

\pagebreak

\pars{Psalmus 2.}

\adventAntiphonaII

\scriptura{Psalmus 112.}

\includescore{temporalia/advent-vespers/ps112-initium-i-g-auto.tex}

\psalmusEtTranslatioB{temporalia/advent-vespers/ps112-i-g.tex}{temporalia/advent-vespers/ps112-boh.tex}{10cm}

\vfill

\pagebreak

\pars{Psalmus 3.}

\adventAntiphonaIII

\scriptura{Psalmus 121.}

\includescore{temporalia/advent-vespers/ps121-initium-viii-G-auto.tex}

\psalmusEtTranslatioB{temporalia/advent-vespers/ps121-viii-g.tex}{temporalia/advent-vespers/ps121-boh.tex}{9.5cm}

\vfill

\pagebreak

\pars{Psalmus 4.}

\adventAntiphonaIV

\scriptura{Psalmus 126.}

\includescore{temporalia/advent-vespers/ps126-initium-i-f-auto.tex}

\psalmusEtTranslatio{temporalia/advent-vespers/ps126-i-f.tex}{temporalia/advent-vespers/ps126-boh.tex}

\vfill

\pagebreak

\pars{Psalmus 5.}

\adventAntiphonaV

\scriptura{Psalmus 147.}

\includescore{temporalia/advent-vespers/ps147-initium-viii-c-auto.tex}

\psalmusEtTranslatioB{temporalia/advent-vespers/ps147-viii-c.tex}{temporalia/advent-vespers/ps147-boh.tex}{10cm}

\vfill

\pars{Capitulum}

\scriptura{Is. 11,1-2}

\includescore{cantus/arom12/capitulum-EgredieturVirga.tex}

\pagebreak

\pars{Hymnus}

\rubrica{Prima stropha sequentis Hymni dicitur flexis genibus.}

\superInitialam{VII}
\includescore{temporalia/hymnus-AveMarisStella.tex}

\vspace{1cm}

\includescore{cantus/arom12/versiculus-DiffusaEst.tex}

\vfill

\pagebreak

\pars{Canticum B. Mariæ Virginis}

\adventAntiphonaSpiritusSanctus

\scripturaMagnificat

\includescore{../../tonipsalmorum/arom12/magnificat-initium-viii-G.tex}

\canticumMagnificatEtTranslatio{temporalia/advent-vespers/magnificat-viiisoll-g.tex}

\vfill

\pagebreak

\label{vesperaefinisadvent}

\inFineHorarumInAdventu

\vfill
