% In Adventu.

\hora{Ad Laudes.} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\rubricaLaudesPrincipium

\vfill

\pars{Psalmus 1.}

\adventAntiphonaI

\scriptura{Psalmus 92.}

\includescore{temporalia/advent-laudes/ps92-initium-viii-G-auto.tex}

\psalmusEtTranslatioB{temporalia/advent-laudes/ps92-viii-g.tex}{temporalia/advent-laudes/ps92-boh.tex}{11cm}

\vfill

\pagebreak

\pars{Psalmus 2.}

\adventAntiphonaII

\scriptura{Psalmus 99.}

\includescore{temporalia/advent-laudes/ps99-initium-i-g-auto.tex}

\psalmusEtTranslatioB{temporalia/advent-laudes/ps99-i-g.tex}{temporalia/advent-laudes/ps99-boh.tex}{11cm}

\vfill

\pagebreak

\pars{Psalmus 3.}

\adventAntiphonaIII

\scriptura{Psalmus 62.}

\includescore{temporalia/advent-laudes/ps62-initium-viii-G-auto.tex}

\psalmusEtTranslatio{temporalia/advent-laudes/ps62-viii-g.tex}{temporalia/advent-laudes/ps62-boh.tex}

\vfill

\pagebreak

\pars{Canticum trium puerorum.}

\adventAntiphonaIV

\scriptura{Dan. 57-88 et 56.}

\includescore{temporalia/advent-laudes/dan3-initium-i-f-auto.tex}

\psalmusEtTranslatioB{temporalia/advent-laudes/dan3-i-f.tex}{temporalia/advent-laudes/dan3-boh.tex}{9cm}

\vfill

\pagebreak

\pars{Psalmus 4.}

\adventAntiphonaV

\scriptura{Psalmus 148.}

\includescore{temporalia/advent-laudes/ps148-initium-viii-c-auto.tex}

\psalmusEtTranslatio{temporalia/advent-laudes/ps148-viii-c.tex}{temporalia/advent-laudes/ps148-boh.tex}

\vfill

\pagebreak

\pars{Capitulum}
\scriptura{Is. 11,1-2}

\includescore{cantus/arom12/capitulum-EgredieturVirga.tex}

\hfill\trCapitEgredieturVirga

\vfill

\pars{Hymnus}

\superInitialam{II}
\includescore{temporalia/hymnus-OGloriosaVirginum}

\trHymOGloriosa

\vfill

\includescore{cantus/arom12/versiculus-BenedictaTu}

\trVersBenedictaTu

\pagebreak

\pars{Canticum Zachariæ}

\adventAntiphonaSpiritusSanctus

\scripturaBenedictus

\includescore{temporalia/advent-laudes/benedictus-initium-viiisoll-G-auto.tex}

\canticumBenedictusEtTranslatio{temporalia/advent-laudes/benedictus-viiisoll-g.tex}

\rubricaFinisHoraeAdvent

\laudesAntiphonaBMV
